A Bidirected String Graph Model of Genome Assembly

### 2012-12-04 presentation/presentation.tex
A-statistic slide

>>>>

\begin{frame}{Arrival rate statistic (A-statistic)}
	\begin{itemize}
		\item The {\bf A-statistic} $A(e)$ of an edge $e$ in a
		bidirected string graph is:
	\end{itemize}
	\[ A(e) = \frac{n}{G} \Delta - \log_2{k} \]
	where $n$ is the total number of reads, $G$ is the estimated genome
	length, $\Delta$ is the length of the edge in bp, and $k$ is the number
	of reads that support that edge.
	\begin{itemize}
		\item The A-statistic is the logarithm of the probability that
		an edge represents unique sequence rather than duplicate
		sequence.
	\end{itemize}
\end{frame}
